Dear All, 

I hope this notes finds you well. 

This email is just to let you know I am currently intending to submit a JWST Director's Discretionary Early Release Science (DD ERS) 
program (deadline Friday Aug 18, 2017). As such, a Notice of Intent (NoI) is required, the deadline for which is, Friday, March 3rd, 2017, 
i.e. two weeks from today:
	https://jwst-docs.stsci.edu/display/JSP/JWST+Director%27s+Discretionary+Early+Release+Science+Call+for+Proposals
The DD ERS Proposal Policies can be found here:
	https://jwst-docs.stsci.edu/display/JSP/JWST+DD+ERS+Proposal+Policies

The general plans is to be present in two of the research areas spanning the science themes of JWST, 
that is: First Light and Reionization, and The assembly of galaxies. The more specific science case will 
focus on six particular themes and questions:
	— Active Black Holes in very high-z galaxies 
	— Evidence for the Transition Mass that quenches AGN activity 
	— What triggers luminous QSO acticity at Cosmic Noon? 
	— Extremely Red Quasars  
	— Changing Look Quasars 
	— True Type 2 QSOs at high redshift

A ‘sketchy' first draft of the overview of the anticipated proposal is attached. 
This is not to exceed 300 words, and should contain: 
(i) the proposed types of JWST observations and science goals and, 
(ii) how the proposed project supports the DD ERS goals and principles. 

The NoI, plus the embryonic version of a longer 5-6 page, science case can 
be found here:
	https://github.com/d80b2t/JWST_ERS
I’ll be the first to admit this science case, including the details of the observing program and designating targets 
needs a tonne of work. However, I was very keen to get this 'out in the wild’, with ample time for potential iterations
before the NoI deadline. 

At this time, I’d naturally welcome any and all suggestions, comments, discussion and questions. 
Obviously, please, do not hesitate to let me know if you are potentially interested in being a co-Investigator
here, and if so, at what level of commitment. 

Finally, this is very much an ‘open source project’ in spirit, so forwarding this email, and/or circulating the GitHub 
link is encouraged. 

Yours,
Nic


====================================
  Dr. Nicholas P. Ross
  STFC Ernest Rutherford Fellow
  Institute for Astronomy
  University of Edinburgh
  Royal Observatory, Blackford Hill 
  Edinburgh EH9 3HJ, United Kingdom
  +44 (0)131-668 8351
  www.roe.ac.uk/~npross/
  github.com/d80b2t/
====================================


